An Imaging Search for Post-MS Companions of Sirius B

### 2021-11-03 paper/paper.tex
add debes ref and small grammar fixes

\section{Introduction} \label{sec:intro}

\begin{itemize}
    \item add Debes text
    \item run through python scripts/grammarly
    \item reorganize Zenodo sections
    \item remove extra references
    \item compile latex diff
    \item add comments to latex diff referencing referee report
\end{itemize}

@@

The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs. As the MS star runs out of Hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius. When Helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation. Eventually the star will run out of fuel and conclude its nuclear burning and become a WD. The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.

@@

\textbf{John Debes work from 2000-2010 with Spitzer, HST}

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade. In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}). We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).

\section{Directly imaging post-MS systems} \label{sec:imaging}

@@

% \section{Post-MS evolution} \label{sec:post-ms}

@@

\section{Sirius B and the Sirius system} \label{sec:sirius}

@@

There have been many attempts to find planets in the Sirius system, but so far no planets have been detected. \citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond}, but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric uncertainty down to $\sim$\qty{10}{\milliarcsecond}. The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}. Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}. A planetary atmosphere and evolution model needs to be chosen in order to derive mass sensitivity limits from imaging. Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}) biasing direct comparisons of mass limits. These studies combined reported sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).  \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reported a sensitivity of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}). \citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs, which ruled out evidence for significant infrared excess from massive disks around Sirius B. \citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reporting sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathakHighContrastImaging2021} took coronagraphic mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A which contained Sirius B in the FOV. Because of the simultaneous observation, their contrast had an azimuthal dependence. Their average reported sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

\section{Observations} \label{sec:obs}
\defcitealias{bonnet-bidaudADONISHighContrast2008a}{BB08}
\defcitealias{bondSiriusSystemIts2017}{B17}
\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
\defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
\begin{deluxetable}{cccc}
    \tablecaption{Parameters of the Sirius system adopted in this study.\label{tbl:system}}
    \tablehead{
        \colhead{parameter} & \colhead{value} & \colhead{unit} & \colhead{ref.}
    }
    \startdata
    $t_\mathrm{sys}$ & 225 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
    $a$ & \num{20.016\pm0.014} & \unit{\au} & \citetalias{bondSiriusSystemIts2017} \\
    \cutinhead{Sirius A}
    $M_\star$ & \num{2.063\pm0.023} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    \cutinhead{Sirius B}
    $M_\star$ & \num{1.018\pm0.011} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    $M_\mathrm{MS}$ & \num{5.1\pm1.1} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
    $t_\mathrm{WD}$ & 126 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017}\\
    $m^{\mathrm{L}^\prime}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
    $M^{\mathrm{L}^\prime}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
    \enddata
\end{deluxetable}

@@

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{psf}
    \caption{The median frame from the second epoch showing the instrumental PSF. The inner core has a Gaussian FWHM of $\sim$\qty{76}{\milliarcsecond}. The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry coinciding with the hexagonal shape of the primary mirror.}
    \label{fig:psf}
\end{figure}

@@

During each observation, we took dark frames and sky-flat frames for calibration. All observations were taken with the large hexagonal pupil maskand with the telescope's field rotator set to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}. In order to avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.

\section{Analysis} \label{sec:analysis}

@@

\section{Results} \label{sec:results}

\begin{figure*}
    \centering
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The annular PCA curve is cut off because the innermost annulus was not able to detect a 100 S/N companion with 5$\sigma$ significance.}
    \label{fig:contrast}
\end{figure*}

\begin{figure*}
    \centering
    \plotone{mass_curves}
    \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the most sensitive contrast. The limits are calculated assuming an \Lp absolute magnitude for Sirius B of \num{11.9}. Both curves are truncated at \qty{1.5}{\au} due to the dynamical stability limit. \textbf{(a)} The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing. The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits. The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{126}{\mega\year}). The relative difference between the ages comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}. \textbf{(b)} The absolute magnitudes are converted to masses using the Sonora Bobcat grid with solar metallicity (solid lines) and with +\qty{0.5}{dex} metallicity (dotted lines). For clarity, only the Gaussian contrast curves are shown in this panel. The two isochrone ages are shown as well, although the Sonora grid cuts off below \qty{200}{\kelvin}, which causes the cutoffs around \qty{1}{\jupitermass}. The relative difference due to the metallicity is $\sim$\qty{0.1}{\jupitermass}.}
    \label{fig:mass-curves}
\end{figure*}

We determined the best-performing algorithms for each epoch using the contrast curves described in \Cref{sec:analysis}. For the first two epochs, full-frame median subtraction had the best contrast at almost all separations. For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}. This algorithm was unable to detect a 100 S/N companion injected into the innermost annulus with 5$\sigma$ significance. The contrast for this innermost annulus is therefore not plotted. The collapsed residual frames from each epoch are shown in \Cref{fig:residuals}, along with the Gaussian significance maps and STIM maps (\Cref{fig:detection}).

The contrast maps from the best performing algorithm for each reduction are shown in \Cref{fig:contrast}. We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.01 (adapted from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}. We divide \Cref{fig:contrast} into two regimes: speckle-limited and background-limited. The speckle-limited regime exists from \qtyrange{0.2}{1}{\au} characterized by the increasing sensitivity with separation. Here we reach a median 5$\sigma$ detection limit of $\sim$19 magnitude (\Lp). This regime is constrained by the quality of the AO correction and the PSF subtraction method, mainly. The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily constrained by the sky brightness. In this region, we reach 20.3 magnitude (\Lp) in the 2020-11-21 epoch. Our data is background-limited due to the relative brightness of the sky in \Lp (\qty{2.91}{mag\per sq. arcsec}\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc2/sensitivity.html}}) compared to the pixel-to-pixel noise sources (e.g., read noise).

@@

In order to convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid. This is not a trivial task, as the effects of post-MS stellar evolution on planets are highly uncertain and not readily modeled in the currently available grids. In particular, we want to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds. We start with the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} for our solar metallicity model. Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which have been shown to better model very cool objects than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}. The ATMO2020 models are not available for non-solar metallicities, yet, so we also employ the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicity.

@@

\section{Discussion \& Conclusions} \label{sec:conclusion}

@@

Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach exceptional detection limits. We took the WD sample from \citet{holberg25ParsecLocal2016} and look at binary systems. The median distance of this subset is \qty{20}{\parsec}. In this work, our inner working angle due to the stellar PSF was $\sim$\qty{80}{\milliarcsecond}, which would be a projected separation of \qty{1.6}{\au} at \qty{20}{\parsec}. The median R magnitude is $\sim$\num{15.2}, though, which may prove challenging for natural guide star AO. However, with laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude increases significantly ($m^R\lesssim$ \num{19}). We suspect future work using LGS AO is capable of studying WD systems at the sub-AU and sub-Jupiter-mass scales. Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the MS.

@@

\section{Data and code availability} \label{sec:data}
All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository\footnote{\url{https://github.com/mileslucas/sirius-b}}. This code includes all of the scripts for generating each figure in this manuscript. The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}}. We hope that this improves the reproducibility of the work as well as providing data for future investigations. Please reach out to the corresponding author for further inquiries regarding data and code availability.

@@

\section{ADI processing results} \label{sec:adi-results}

@@

\clearpage
\section{Provisional orbit fitting} \label{sec:orbits}

>>>>

\section{Introduction}\label{sec:intro}

@@

The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs. As the MS star runs out of hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius. When helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation. Eventually the star will run out of fuel and conclude its nuclear burning and become a WD. The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.

@@

Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts. We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade. In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}). We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}). We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}). Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).

\section{Directly imaging post-MS systems}\label{sec:imaging}

@@

% \section{Post-MS evolution}\label{sec:post-ms}

@@

\section{Sirius B and the Sirius system}\label{sec:sirius}

@@

There have been many attempts to find planets in the Sirius system, but so far no planets have been detected. \citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond}, but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric uncertainty down to $\sim$\qty{10}{\milliarcsecond}. The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}. Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}. A planetary atmosphere and evolution model are needed in order to derive mass sensitivity limits from imaging. Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}) biasing direct comparisons of mass limits. These studies combined reported sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).  \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reported a sensitivity of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}). \citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs, which ruled out evidence for significant infrared excess from massive disks around Sirius B. \citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reporting sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathakHighContrastImaging2021} took coronagraphic mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A which contained Sirius B in the FOV. Because of the simultaneous observation, their contrast had an azimuthal dependence. Their average reported sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

\section{Observations}\label{sec:obs}
\defcitealias{bonnet-bidaudADONISHighContrast2008a}{BB08}
\defcitealias{bondSiriusSystemIts2017}{B17}
\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
\defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
\begin{deluxetable}{cccc}
    \tablecaption{Parameters of the Sirius system adopted in this study.\label{tbl:system}}
    \tablehead{
        \colhead{parameter} & \colhead{value} & \colhead{unit} & \colhead{ref.}
    }
    \startdata
    $t_\mathrm{sys}$ & 225 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
    $a$ & \num{20.016\pm0.014} & \unit{\au} & \citetalias{bondSiriusSystemIts2017} \\
    \cutinhead{Sirius A}
    $M_\star$ & \num{2.063\pm0.023} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    \cutinhead{Sirius B}
    $M_\star$ & \num{1.018\pm0.011} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
    $M_\mathrm{MS}$ & \num{5.1\pm1.1} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
    $t_\mathrm{WD}$ & 126 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017}\\
    $m^{\mathrm{L}^\prime}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
    $M^{\mathrm{L}^\prime}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
    \enddata
\end{deluxetable}

@@

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{psf}
    \caption{The median frame from the second epoch showing the instrumental PSF. The inner core has a Gaussian FWHM of $\sim$\qty{76}{\milliarcsecond}. The blobs surrounding the first ring are the speckles, with roughly 6-way radial symmetry coinciding with the hexagonal shape of the primary mirror.}
    \label{fig:psf}
\end{figure}

@@

During each observation, we took dark frames and sky-flat frames for calibration. All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}. In order to avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.

\section{Analysis}\label{sec:analysis}

@@

\section{Results}\label{sec:results}

\begin{figure*}
    \centering
    \plotone{contrast_curves}
    \caption{The contrast curves for the best performing algorithm from each epoch. The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves. The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line. The annular PCA curve cuts off because the innermost annulus was not able to detect a 100 S/N companion with 5$\sigma$ significance.}
    \label{fig:contrast}
\end{figure*}

\begin{figure*}
    \centering
    \plotone{mass_curves}
    \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the most sensitive contrast. The limits are calculated assuming an \Lp absolute magnitude for Sirius B of \num{11.9}. Both curves are truncated at \qty{1.5}{\au} due to the dynamical stability limit. \textbf{(a)} The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing. The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits. The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{126}{\mega\year}). The relative difference between the ages comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}. \textbf{(b)} The absolute magnitudes are converted to masses using the Sonora Bobcat grid with solar metallicity (solid lines) and with +\qty{0.5}{dex} metallicity (dotted lines). For clarity, we only show the Gaussian contrast curves in this panel. The Sonora grid does not have atmospheric spectra for $T_\mathrm{eff}$ \textless \qty{200}{\kelvin}, which causes the cutoffs around \qty{1}{\jupitermass}. The relative difference due to the metallicity is $\sim$\qty{0.1}{\jupitermass}.}
    \label{fig:mass-curves}
\end{figure*}

We determined the best-performing algorithms for each epoch using the contrast curves described in \Cref{sec:analysis}. For the first two epochs, full-frame median subtraction had the best contrast at almost all separations. For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}. This algorithm was unable to detect a 100 S/N companion injected into the innermost annulus with 5$\sigma$ significance. The contrast for this innermost annulus is therefore not plotted. \Crefrange{fig:residuals}{fig:detection} show the collapsed residual frames from each epoch, along with the Gaussian significance maps and STIM maps.

We show the contrast curves from the best performing algorithm for each reduction in \Cref{fig:contrast}. We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.01 (adapted from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}. We divide \Cref{fig:contrast} into two regimes: speckle-limited and background-limited. The speckle-limited regime exists from \qtyrange{0.2}{1}{\au} characterized by the increasing sensitivity with separation. Here we reach a median 5$\sigma$ detection limit of $\sim$19 magnitude (\Lp). This regime is constrained by the quality of the AO correction and the PSF subtraction method, mainly. The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily constrained by the sky brightness. In this region, we reach 20.3 magnitude (\Lp) in the 2020-11-21 epoch. Our data is background-limited due to the relative brightness of the sky in \Lp (\qty{2.91}{mag\per sq. arcsec}\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc2/sensitivity.html}}) compared to the pixel-to-pixel noise sources (e.g., read noise).

@@

In order to convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid. This is not a trivial task, as the effects of post-MS stellar evolution on planets are highly uncertain and not readily modeled in the currently available grids. In particular, we want to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds. We start with the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} for our solar metallicity model. Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which model very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}. The ATMO2020 models are not available for non-solar metallicities, yet, so we also employ the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicity.

@@

\section{Discussion \& Conclusions}\label{sec:conclusion}

@@

Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach exceptional detection limits. We took the WD sample from \citet{holberg25ParsecLocal2016} and analyzed the 7 binary systems. The median distance of this subset is \qty{20}{\parsec}. In this work, our inner working angle due to the stellar PSF was $\sim$\qty{80}{\milliarcsecond}, which would be a projected separation of \qty{1.6}{\au} at \qty{20}{\parsec}. The median R magnitude is $\sim$\num{15.2}, though, which may prove challenging for natural guide star AO. However, with laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude increases significantly ($m^R\lesssim$ \num{19}). We suspect future work using LGS AO is capable of studying WD systems at the sub-AU and sub-Jupiter-mass scales. Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the MS.

@@

\section{Data and code availability}\label{sec:data}

All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript. The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}} We hope that this improves the reproducibility of the work as well as providing data for future investigations. Please reach out to the corresponding author for further inquiries regarding data and code availability.

@@

\section{ADI processing results}\label{sec:adi-results}

@@

\clearpage
\section{Provisional orbit fitting}\label{sec:orbits}
